A Survey of Possible Exoskeleton Control Architectures and Algorithms\\ (Draft 2.1)

### 2015-09-21 control.tex
added half of BLEEX section.
more updates

@@

A useful background paper: \url{http://summerschool.stiff-project.org/fileadmin/pdf/1804_C19.pdf}

@@

One basic distinction is whether the actuators are thought of as position
or force sources. Often this is revealed by the design of the ``low level''
controller. Note that this is often somewhat confusing. Electric motors
are torque sources (low impedance), but when a high gear ratio transmission
is added (such as a harmonic drive) the whole system becomes high impedance
and thus is best thought of as a position (or velocity) source. Therefore,
position control is performed by the low level controller. Hydraulic actuators
are high impedance, but when a force or load sensor is added (or piston differential
oil pressure is used as a force sensor), the whole system becomes low impedance
and is best thought of as a force source. Force (or joint torque) control is
performed by the low level controller. Force or torque can be added to an
electromechanical drive train (electric motor plus gears or motor plus ballscrew)
to make it lower impedance and more like a force source as well.

@@

@@

@@

@@

@@

>>>>

A later white paper will discuss how to handle malfunctions and damage to the
system. Basically this boils down to fault detection, and switchover to
an approapriate safe mode of operation.

@@

A useful background paper on impedance and admittance: \url{http://summerschool.stiff-project.org/fileadmin/pdf/1804_C19.pdf}

@@

One basic distinction is whether the actuators are thought of as position
or force sources. Often this is revealed by the design of the ``low level''
controller. Note that this is often somewhat confusing. Electric motors
are torque sources (low impedance), but when a high gear ratio transmission
is added (such as a harmonic drive) the whole system becomes high impedance
and thus is best thought of as a position (or velocity) source. Therefore,
position or velocity 
control is performed by the low level controller. Hydraulic actuators
are high impedance, but when a force or load sensor is added (or piston differential
oil pressure is used as a force sensor), the whole system becomes low impedance
and is best thought of as a force source. Force (or joint torque) control is
performed by the low level controller. Force or torque sensing can be added to an
electromechanical drive train (electric motor plus gears or electric
motor plus ballscrew)
to make it lower impedance and more like a force source as well.

@@

\section{Test case: Atlas humanoid robot}

Gazebo and SDFast models.

@@

\subsection{Full Atlas robot implementation.}

@@

DISCUSS HOW TO HANDLE SENSOR NOISE

@@

\subsection{Full Atlas robot.}

\section{Robustness to parametric modeling error}

\section{Robustness to unmodeled dynamics}

\subsection{Example unmodeled dynamics}

Examples:
\begin{itemize}
\item
A) hydraulic actuator dynamics.
\item
B) delay. 
\item
C) elastic straps sinusoidal oscillation.
\item
D) loose straps (bang coast bang oscillation)
\end{itemize}

\subsection{1 joint rotary example.}

\subsection{2 joint rotary example: stance.}

\subsection{2 joint rotary example: swing.}

\subsection{4 link body example.}

\subsection{Full Atlas robot.}

\section{Underactuated control}.

Not talking about floating body dynamics, where global (``root'') position
and velocity is unactuated.

What about only sagittal actuation?

\subsection{No actuation on lateral and twist}

\subsection{Passive actuation on lateral and twist}

Address what is the complexity penalty, weight penalty, 
and ``drag'' of actuator on individual joint motion.

\subsection{Active actuation on lateral and twist}

Address what is the complexity penalty, weight penalty, 
and ``drag'' of actuator on individual joint motion.

@@

sensitivity to
 modeling error
 sensor error
 unmodeled dynamics

underactuated control problem
 - not fully actuated sagittal only.
 - how necessary is lateral actuation
 - what is the penalty
  weight
  drag of actuator

how handle failure and damage after Oct 1

what about a full model of the system

Oct 5-9
